How many researchers use 'boilerplate' statistical analysis sections?

### 2021-03-09 manuscript/draft_manuscript.Rmd
Update draft_manuscript.Rmd

>>>>

Top matches (Topic 5)
* 10.1371/journal.pone.0120046: Statistical analysis was performed using the SPSS version 18.0 (SPSS Inc., Chicago, IL, USA). Mann-Whitney test was used for the analysis of continuous variables. Chi-square test, Fisher’s exact test or one-way ANOVA test was employed for the analysis of categorical variables. P < 0.05 was considered statistically significant.

* 10.1371/journal.pone.0204950: Statistical analyses were performed using SPSS version 20.0 for Windows (SPSS Inc., Chicago, IL). Categorical and continuous variables were evaluated with the non-parametric chi-square test, the Kruskal-Wallis test, and the Mann-Whitney U test. All statistical tests were two-sided, and a p value <0.05 was considered statistically significant.

* 10.1371/journal.pone.0062685: SPSS version 21.0 for Windows (SPSS, Inc., Chicago, IL, USA) was used for statistical analysis. Categorical variables were analyzed by a chi-square test or Fisher’s exact test. Continuous variables were analyzed by independent t-test or Mann-Whitney test. Logistic regression analysis was performed to evaluate the effects of independent variables on clinical outcomes. A p-value of <0.05 by the two-tailed test was considered statistically significant.

* 10.1371/journal.pone.0133783: Data are expressed as means ± SD or medians (with interquartile ranges). Statistical analyses were performed using SPSS software version 19.0 (SPSS, Inc., Chicago, IL, USA). Statistical significance for intergroup differences was assessed by the χ2 test or Fisher’s exact test for categorical variables, and by the Student’s t-test, or Mann–Whitney U test for continuous variables. Correlations between variables were tested with Spearman’s correlation analysis. A P-value <0.05 was considered significant for all tests.

* 10.1371/journal.pone.0098797: Univariate analysis was performed using Mann–Whitney U-tests for continuous variables and Pearson's chi-square or Fisher's exact tests for categorical variables. Statistical significance was set at a P-value <0.05. SPSS statistical software version 19 (SPSS, Chicago, IL, USA) was used to perform the statistical analyses.
